%!TEX root = ../todd-cv.tex
%----------------------------------------------------------------------------------
%        Research Experience
%----------------------------------------------------------------------------------
\section{Research and Work Experience}
	\cventry{2018-present}
		{\href{https://www.nvidia.com/en-us/}{Nvidia}}
		{Senior Architect}
		{}{}
		{
		\begin{itemize}
		\item Develop performance prediction models and tools for HPC applications.
    \item Research and propose new architecture features for next generation
    GPUs.
		\end{itemize}
	  }
	\cventry{2016-2018}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}
		{Computer Scientist (from 03/18), Fernbach Postdoctoral Fellow (till 03/18)}
		{}{}
		{
		\begin{itemize}
		\item Researched and characterized communication throughput of HPC networks.
    \item Developed data analytics driven methods for performance optimization.
		\end{itemize}
	  }
	\cventry{2011-2016}
		{\href{https://cs.illinois.edu}{Dept of Computer Science}, University of Illinois at Urbana-Champaign}
		{Research Assistant}
		{}{}
		{
		\begin{itemize}
    \item Created \href{https://github.com/LLNL/tracer}{TraceR} and contributed
    to \href{https://xgitlab.cels.anl.gov/codes/codes}{CODES} for scalable simulation of parallel codes on HPC networks.
    %\item Proposed \href{https://github.com/LLNL/damselfly}{Damselfly} - a fast
    %analytical model for understanding performance of dragonfly networks.
    \item Developed new features for
    \href{https://charm.cs.illinois.edu}{Charm++}, a widely used parallel programming model.
    \item Contributed to development and performance improvements in
    \href{http://charm.cs.illinois.edu/OpenAtom/}{OpenAtom} and \href{http://www.ks.uiuc.edu/Research/namd}{NAMD}.
		\end{itemize}
    }

  \cventry{Summer 2014}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}
		{Research Intern}
		{}{}
		{Analyzed prediction models to identify factors that affect performance on HPC networks.}

	\cventry{Summer 2012}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}
		{Research Intern}
		{}{}
		{Proposed and demonstrated use of machine learning based models for predicting communication
    performance of HPC applications.}

  \cventry{Spring 2011}
		{\href{https://cs.illinois.edu}{Dept of Computer Science}, University of Illinois at Urbana-Champaign}
		{Visiting Scholar}
		{}{}
		{Re-designed runtime-level memory management module for speed and efficiency in Charm++.}

	\cventry{2009-2011}
		{\href{http://www.research.ibm.com/labs/india}{IBM Research}, India}
		{Blue Scholar}
		{}{}
		{Developed 3$\times$ faster topology-aware algorithms for collective communication on Blue Gene systems.}

\iftoggle{resume}{}{
  % Skip for resume
	\cventry{Summer 2007}
		{Polytechnic Institute of NYU}
		{Undergraduate Research Intern}
		{}{}
		{Investigated use of obfuscation methods in logic design.}
}

%	\cventry{Summer 1999}
%		{\href{http://physics.ncsu.edu/}{NCSU Physics Department}}
%		{Summer Research Assistant}
%		{}{}
%		{Designed imaging algorithms and an archival website for the Diffraction
%		 Enhanced Imaging (DEI) Group.}
