%!TEX root = ../todd-cv.tex
%----------------------------------------------------------------------------------
%            Software Projects
%----------------------------------------------------------------------------------
\section{Software Projects}
%
% By me
%
%\subsection{Developed by me}
	\cvitem{\github{traceR}}{
		Trace-driven PDES-based network simulation of parallel applications.
  }
	\cvitem{\github{Damselfly}}{
		Analytical modeling of steady-state traffic flow on dragonfly networks.
  }
	\cvitem{\github{bgqncl}}{
		An easy interface for network counters collection on BlueGene/Q systems.
  }
	\cvitem{\href{https://charm.cs.illinois.edu/gerrit/gitweb?p=benchmarks\%2Fleanmd.git;a=summary}{LeanMD}}{
	  A mini-application for exploring optimizations for molecular dynamics.
  }
	\cvitem{\href{https://charm.cs.illinois.edu/gerrit/gitweb?p=topoAPI.git;a=summary}{topoAPI}}{
		Fully-automated profiling, analysis, and mapping on HPC systems.
  }
	\cvitem{\href{https://charm.cs.illinois.edu/gerrit/gitweb?p=ross.git;a=summary}{Charm-ROSS}}{
		Charm++ based implementation of the parallel discrete event simulator ROSS.
  }
%
%
%
\subsection{Open-source software I contribute to}
	\cvitem{\href{https://xgitlab.cels.anl.gov/codes/codes}{CODES}}{
		Packet-level HPC network simulation.
  }
	\cvitem{\href{https://charm.cs.illinois.edu}{Charm++}}{
		Object-based message driven parallel programming paradigm.
  }
	\cvitem{\href{http://charm.cs.illinois.edu/OpenAtom/}{OpenAtom}}{
		Scalable Ab-Initio Molecular Dynamics with diverse features.
  }
	\cvitem{\href{http://charm.cs.uiuc.edu/research/episim}{EpiSimdemics}}{
    Hybrid contagion modeling using Charm++.
  }
	\cvitem{\href{https://github.com/carothersc/ROSS}{ROSS}}{
    Scalable parallel discrete simulation with optimistic execution.
  }
	\cvitem{\href{http://www.ks.uiuc.edu/Research/namd/}{NAMD}}{
    Highly scalable parallel molecular dynamics.
  }
